Sparse spectral and $p$-finite element methods for partial differential equations on disk-slices and trapeziums

### 2019-04-11 papers/halfdisk/halfdisk.tex
New figures

\begin{figure}
	\begin{subfigure}[t]{0.45\textwidth}
	\includegraphics[scale=0.4]{sparsityoflaplacian-w11}
	\end{subfigure}
	\begin{subfigure}[t]{0.45\textwidth}
	\includegraphics[scale=0.4]{sparsityoflaplacian-w22}
	\end{subfigure}
	\begin{subfigure}[t]{0.45\textwidth}
	\includegraphics[scale=0.4]{sparsityoflaplacian-00}
	\end{subfigure}
	\begin{subfigure}[t]{0.45\textwidth}
	\includegraphics[scale=0.4]{sparsityofhelmholtz}
	\end{subfigure}
	\centering
    	\caption{\sotodoinline{Fix titles} "Spy" plots of the different operator matrices for the Laplacian operator $\Delta$, as well as the operator matrix for the Helmholtz equation, showing their sparsity. Top Left: $\laplacewii$. Top Right: $\laplacewtt$. Bottom Left: $\laplaceoo$. Bottom Right: the weighted variable coefficient Helmholtz operator $\laplacewii + k^2 \: T^{(0,0)\to(1,1)} \: V({J_x^{(0,0)}}^\top, {J_y^{(0,0)}}^\top) \: T_W^{(1,1)\to(0,0)}$ for $v(x,y) = xy^2$ and $k = 0.25$.}
        \label{fig:sparsity}
\end{figure}

>>>>

\begin{figure}
	\centering
	\begin{subfigure}[t]{0.3\textwidth}
	\centering
	\includegraphics[scale=0.35]{sparsityoflaplacian-w11}
	\end{subfigure}
	\begin{subfigure}[t]{0.3\textwidth}
	\centering
	\includegraphics[scale=0.35]{sparsityofhelmholtz}
	\end{subfigure}
	\begin{subfigure}[t]{0.3\textwidth}
	\centering
	\includegraphics[scale=0.35]{sparsityofbiharmonic}
	\end{subfigure}
    	\caption{"Spy" plots of (differential) operator matrices, showing their sparsity. Left: the Laplace operator $\laplacewii$. Centre: the weighted variable coefficient Helmholtz operator $\laplacewii + k^2 \: T^{(0,0)\to(1,1)} \: V({J_x^{(0,0)}}^\top, {J_y^{(0,0)}}^\top) \: T_W^{(1,1)\to(0,0)}$ for $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 200$. Right: the biharmonic operator $\biharmonic$.}
        \label{fig:sparsity}
\end{figure}
